The core transcriptome of mammalian placentas and the divergence of expression with placental shape

### 2017-02-20 manuscript/manuscript.Rnw
add limitations section
Add limitations section to address a reviewer critique. Additionally
fix a time point typo.

@@

This study has identified many tantalizing molecular pathways which
illuminate the vast diversity of placental morphology and may explain
some placental malfunctions in \human{}. However, the strength of our
hypotheses are limited by our limited data; more placentas from
multiple members of diverse clades and different timepoints are still
needed to come to a more complete understanding of the genomic and
molecular basis for placenta morphology and function. We look forward
to collecting and analyzing such a dataset.

>>>>

\subsection{Limitations}

This study includes only term placentas, and our conclusions are
limited to the set of genes which continue to be expressed at term. We
suspect that many genes which are responsible for establishing shape,
intimacy, and interdigitation are expressed and function at earlier
time points where placental morphology is being established.
Furthermore, while these samples have been dissected to only include
the fetal interface, they likely include substantial cell and tissue
heterogeneity. We are therfore not yet able to assign specific genes
in our core placental transcriptome to specific cell types and
tissues. We believe that samples of placentas from earlier in
gestation and from multiple locations within the placenta and at
multiple will address these limitations.

@@

This study has identified many tantalizing molecular pathways which
illuminate the vast diversity of placental morphology and may explain
some placental malfunctions in \human{}. However, the strength of our
hypotheses are limited by our limited data; more placentas from
multiple members of diverse clades and different time points are still
needed to come to a more complete understanding of the genomic and
molecular basis for placenta morphology and function. We look forward
to collecting and analyzing such a dataset.
